My Cool Title

### 2019-05-03 paper.tex
Fixed syntax issues

\noindent where $\mathbf{S}$ represents the agent's state space, $\mathbf{A}$ is a set of actions the agent can execute in any state, $\mathbf{T}$ is a table containing the probabilities of transitioning from state $s$ to state $s'$, $s, s' \in \mathbf{S}$ after executing action $a$, $a \in \mathbf{A}$ and $\mathbf{R}$ is the reward the agent receives for reaching state $s'$ after executing action $a$. $\mathbf{\Omega}$ is a set of possible state observations the agent can make, while the table $\mathbf{O}$ contains the probabilities of making state observation $\omego$, $\omega \in \mathbf{\Omega}$, when in state $s$ after executing action $a$. Finally, the scalar $\gamma$ is a discount factor that prioritises long-term over short-term rewards and affects the model's convergence rate.

@@

$\mathbf{T}$ was determined by extracting the inter-object spatial relationships for the objects of interest in terms of the actions in $\matbf{A}$ from the OpenImages\todo{cite} dataset. 
For example, by iterating over all of the images containing the objects of interest, we can see that the object `monitor' is located above (i.e. UP) the object `keyboard' in 87\% \todo{get real percentage} of images containing both objects. 
The transition function for this case will look like

>>>>

\noindent where $\mathbf{S}$ represents the agent's state space, $\mathbf{A}$ is a set of actions the agent can execute in any state, $\mathbf{T}$ is a table containing the probabilities of transitioning from state $s$ to state $s'$, $s, s' \in \mathbf{S}$ after executing action $a$, $a \in \mathbf{A}$ and $\mathbf{R}$ is the reward the agent receives for reaching state $s'$ after executing action $a$. $\mathbf{\Omega}$ is a set of possible state observations the agent can make, while the table $\mathbf{O}$ contains the probabilities of making state observation $\omega$, $\omega \in \mathbf{\Omega}$, when in state $s$ after executing action $a$. Finally, the scalar $\gamma$ is a discount factor that prioritises long-term over short-term rewards and affects the model's convergence rate.

@@

$\mathbf{T}$ was determined by extracting the inter-object spatial relationships for the objects of interest in terms of the actions in $\mathbf{A}$ from the OpenImages\todo{cite} dataset. 
For example, by iterating over all of the images containing the objects of interest, we can see that the object `monitor' is located above (i.e. UP) the object `keyboard' in 87\% \todo{get real percentage} of images containing both objects. 
The transition function for this case will look like
